---
title: "Schools"
author: "Jatin"
date: "18/04/2021"
params:
  orig_date: "Original Publish Date: 18th April, 2021"
  update_date: !r paste("Updated on:", format(Sys.time(), '%d %B, %Y'))
authors:
  - jatin
summary: School Data Analysis
output:
  html_document:
    theme: flatly
    toc: TRUE
    toc_float: TRUE
    toc_depth: 5
    number_sections: TRUE
    fig_width: 6            
editor_options: 
  chunk_output_type: inline

---



### Document History

`r params$orig_date`

`r params$update_date`

---

```{r set up, warning=FALSE, include=FALSE, message= FALSE}
knitr::opts_chunk$set(cache = FALSE ,echo = FALSE, message=FALSE, warning = FALSE,fig.width = 16/2, fig.height = 9/2)
library(tidyverse)
library(data.table)
library(knitr)
library(kableExtra)
library(scales)
library(gridExtra)
library(stargazer)
library(ggbump)
library(cowplot)
library(colorspace)
library(ggthemes)
library(DT)
install.packages("data.table")
library(data.table)
library(widgetframe)
`%!in%` = Negate(`%in%`)
select <- dplyr::select
```
---



# DISE DATA UP

Intially it contained 2,95,721 schools.But after removing those schools whose year of establishment not given correctly and subsetting the year range between 1977 and 2019 we got 175820 schools and merging it with dynasty dataset we got 171936 schools

```{r}
college_up <- fread("C:/Users/Jatin/Downloads/JatinCPR/Jatin NEW CPR/SCHOOL DATA NEW/sch_final.csv")

#Hmisc::describe(college_up)
```


### Main variables

```{r}
names(college_up)
```

### types of management


```{r}
library(data.table)
library(dplyr)
college_up <- fread("C:/Users/Jatin/Downloads/JatinCPR/Jatin NEW CPR/SCHOOL DATA NEW/sch2.csv")
college_up %>% group_by(School_New_Management) %>% summarise(count = n())
```

### Year by year break-up of number of Schools
Private Unaided as Private and Madarsa Unrecogonized,Unrecogonized schools as others,and all remaining schools as Government


```{r}
library(data.table)
library(dplyr)
college_up <- fread("C:/Users/Jatin/Downloads/JatinCPR/Jatin NEW CPR/SCHOOL DATA NEW/sch_3.csv")
college_up  %>% 
    ggplot(aes(factor(Yeur_Estd), college_up$`Unnamed: 0`, fill =Sch_New_Final_Management))+
    geom_bar(position = "stack",stat = "identity")+
    labs(x = "Year",y='Schools Established')+
    theme_minimal()+
    theme(#axis.text.x = element_text(angle = 90),
        #legend.position = "bottom", 
        axis.text.y = element_text(size = 7))+
    coord_flip()

 
```

### breakup of election year school established


```{r}
library(data.table)
library(dplyr)
college_up <- fread("C:/Users/Jatin/Downloads/JatinCPR/Jatin NEW CPR/SCHOOL DATA NEW/merge_school.csv")
college_up %>% group_by(year) %>%     
  summarise_at(vars(n_schools),  
               list(schools_established = sum)) 
```

## REGRESSION FROM 1977-2013

```{r,warning=FALSE,results='asis',echo=FALSE,include=TRUE,message=FALSE}
library(plm)
library(stargazer)
firstphase<-readr::read_csv("C:/Users/Jatin/Downloads/JatinCPR/Jatin NEW CPR/SCHOOL DATA NEW/merge_school.csv")
firstphase<-readr::read_csv("C:/Users/Jatin/Downloads/JatinCPR/Jatin NEW CPR/SCHOOL DATA NEW/merge_school.csv")

firstphase.p<-pdata.frame(firstphase,index=c("year"))
first_phase_model.p<-plm(n_schools~dyn_cum_2+caste_groups,data=firstphase.p)
second_phase_model_logit<-glm(data =firstphase.p, n_schools~dyn_cum_2+caste_groups)
second_phase_model_poisson<-glm(data =firstphase.p, n_schools~dyn_cum_2+caste_groups,family =  "quasipoisson")


stargazer(first_phase_model.p,second_phase_model_logit,second_phase_model_poisson,column.labels=c("OLS","LOGIT","POISSON"),no.space=TRUE,align=TRUE,type = 'html',add.lines=list(c('Year fixed effects', 'Yes','Yes','Yes')))
```

## REGRESSION FROM 1991-2013

```{r,warning=FALSE,results='asis',echo=FALSE,include=TRUE,message=FALSE}
library(plm)
library(stargazer)

firstphase<-readr::read_csv("C:/Users/Jatin/Downloads/JatinCPR/Jatin NEW CPR/SCHOOL DATA NEW/mergedfnew.csv")

firstphase.p<-pdata.frame(firstphase,index=c("year"))
first_phase_model.p<-plm(n_schools~dyn_cum_2+caste_groups,data=firstphase.p)
second_phase_model_logit<-glm(data =firstphase.p, n_schools~dyn_cum_2+caste_groups)
second_phase_model_poisson<-glm(data =firstphase.p, n_schools~dyn_cum_2+caste_groups,family =  "quasipoisson")


stargazer(first_phase_model.p,second_phase_model_logit,second_phase_model_poisson,column.labels=c("OLS","LOGIT","POISSON"),no.space=TRUE,align=TRUE,type = 'html',add.lines=list(c('Year fixed effects', 'Yes','Yes','Yes')))
```

## REGRESSION FROM 1991-2013(PRIVATE)

```{r,warning=FALSE,results='asis',echo=FALSE,include=TRUE,message=FALSE}
library(plm)
library(stargazer)

firstphase<-readr::read_csv("C:/Users/Jatin/Downloads/JatinCPR/Jatin NEW CPR/SCHOOL DATA NEW/private.csv")

firstphase.p<-pdata.frame(firstphase,index=c("year"))
first_phase_model.p<-plm(n_schools~dyn_cum_2+caste_groups,data=firstphase.p)
second_phase_model_logit<-glm(data =firstphase.p, n_schools~dyn_cum_2+caste_groups)
second_phase_model_poisson<-glm(data =firstphase.p, n_schools~dyn_cum_2+caste_groups,family =  "quasipoisson")


stargazer(first_phase_model.p,second_phase_model_logit,second_phase_model_poisson,column.labels=c("OLS","LOGIT","POISSON"),no.space=TRUE,align=TRUE,type = 'html',add.lines=list(c('Year fixed effects', 'Yes','Yes','Yes')))


```{r,warning=FALSE,results='asis',echo=FALSE,include=TRUE,message=FALSE}
