---
title: Banks Dynasty Analysis
author: ''
date: '2021-04-24'
slug: banks-dynasty-analysis
categories: []
tags: []
---

------------------------------------------------------------------------


## Main Variables UP Analysis

------------------------------------------------------------------------
There were total of 8057 Banks.But some were established before than 1977 and so after merging there are total now 7351 banks.
------------------------------------------------------------------------
```{r,echo=FALSE,include=TRUE,message=FALSE,warning=FALSE}
#install.packages("kableExtra")
#install.packages("magrittr") # package installations are only needed the first time you use it
#install.packages("dplyr")    # alternative installation of the %>%
library(magrittr) # needs to be run every time you start R and want to use %>%
library(dplyr)
totalseats<-readr::read_csv('C:/Users/Jatin/Downloads/JatinCPR/Jatin NEW CPR/RBI NEW DATA/rbi_data_22_03.csv')
totalseats <- subset(totalseats,select=-c(X1,AC,Country,date,geometry,Latitude,lgd_district_id,lgd_district_name,lgd_state_name,Longitude,month,PC,pc11_district_id,pc11_district_name,pc11_state_id,pc11_state_name,pc11_town_id,pc11_village_id))
ls(totalseats)

```
------------------------------------------------------------------------
TYPE OF RBI BANK GROUPS

------------------------------------------------------------------------


```{r,echo=FALSE,include=TRUE,message=FALSE,warning=FALSE}
#install.packages("kableExtra")
#install.packages("magrittr") # package installations are only needed the first time you use it
#install.packages("dplyr")    # alternative installation of the %>%
library(magrittr) # needs to be run every time you start R and want to use %>%
library(dplyr)
totalseats<-readr::read_csv('C:/Users/Jatin/Downloads/JatinCPR/Jatin NEW CPR/RBI NEW DATA/rbi_bank_group.csv')
totalseats <- subset(totalseats,select=-c(X1))
library(kableExtra)

totalseats %>%
  kbl() %>%
  kable_material(c("striped", "hover"),full_width = FALSE)%>%kable_styling(bootstrap_options = "striped")

```
------------------------------------------------------------------------

TYPE OF RBI BANK POPULATION GROUPS

------------------------------------------------------------------------


```{r,echo=FALSE,include=TRUE,message=FALSE,warning=FALSE}
#install.packages("kableExtra")
#install.packages("magrittr") # package installations are only needed the first time you use it
#install.packages("dplyr")    # alternative installation of the %>%
library(magrittr) # needs to be run every time you start R and want to use %>%
library(dplyr)
totalseats<-readr::read_csv('C:/Users/Jatin/Downloads/JatinCPR/Jatin NEW CPR/RBI NEW DATA/rbi_population_group.csv')
totalseats <- subset(totalseats,select=-c(X1))
library(kableExtra)

totalseats %>%
  kbl() %>%
  kable_material(c("striped", "hover"),full_width = FALSE)%>%kable_styling(bootstrap_options = "striped")

```
------------------------------------------------------------------------

## BANKS ESTABLISHED OVER THE ELECTION YEARS

------------------------------------------------------------------------


```{r,echo=FALSE,include=TRUE,message=FALSE,warning=FALSE}
#install.packages("kableExtra")
#install.packages("magrittr") # package installations are only needed the first time you use it
#install.packages("dplyr")    # alternative installation of the %>%
library(magrittr) # needs to be run every time you start R and want to use %>%
library(dplyr)
totalseats<-readr::read_csv('C:/Users/Jatin/Downloads/JatinCPR/Jatin NEW CPR/RBI NEW DATA/rbi_year_group.csv')
totalseats <- subset(totalseats,select=-c(X1))
library(kableExtra)

totalseats %>%
  kbl() %>%
  kable_material(c("striped", "hover"),full_width = FALSE)%>%kable_styling(bootstrap_options = "striped")

```
------------------------------------------------------------------------

TYPE OF BANKS ESTABLISHED GOVERNMENT OR PRIVATE

------------------------------------------------------------------------
Private Sector Banks,Payments Bank,Foreign Bank,Small Finance Bank are grouped into Private Banks
```{r,echo=FALSE,include=TRUE,message=FALSE,warning=FALSE}
#install.packages("kableExtra")
#install.packages("magrittr") # package installations are only needed the first time you use it
#install.packages("dplyr")    # alternative installation of the %>%
library(magrittr) # needs to be run every time you start R and want to use %>%
library(dplyr)
totalseats<-readr::read_csv('C:/Users/Jatin/Downloads/JatinCPR/Jatin NEW CPR/RBI NEW DATA/rbi_type_bank.csv')
totalseats <- subset(totalseats,select=-c(X1))
library(kableExtra)

totalseats %>%
  kbl() %>%
  kable_material(c("striped", "hover"),full_width = FALSE)%>%kable_styling(bootstrap_options = "striped")

```
------------------------------------------------------------------------

TYPE OF BANKS ESTABLISHED YEAR WISE

------------------------------------------------------------------------

```{r,warning=FALSE,echo=FALSE,include=TRUE,message=FALSE}
#install.packages("kableExtra")
#install.packages("magrittr") # package installations are only needed the first time you use it
#install.packages("dplyr")    # alternative installation of the %>%
library(magrittr) # needs to be run every time you start R and want to use %>%
library(dplyr)
library(ggplot2)
totalseats<-readr::read_csv('C:/Users/Jatin/Downloads/JatinCPR/Jatin NEW CPR/RBI NEW DATA/all_type.csv')
totalseats <- subset(totalseats,select=-c(X1))
totalseats$year_y<-as.factor(totalseats$year_y)
ggplot(totalseats,aes(x=totalseats$year_y,y=totalseats$`Unnamed: 0_x`,fill=Type))+geom_col()+coord_flip()+labs(
        y ="Banks Established", x = "Year")
```

--------------------------------------------------------------------

# REGRESSION ON BANKS

-----------------------------------------------------------------
Banks From 1977-2019
```{r,warning=FALSE,results='asis',echo=FALSE,include=TRUE,message=FALSE}
library(plm)
library(stargazer)
firstphase<-readr::read_csv("C:/Users/Jatin/Downloads/JatinCPR/Jatin NEW CPR/RBI NEW DATA/rbi_18_04_2021_up_1.csv")

firstphase.p<-pdata.frame(firstphase,index=c("year_x"))
first_phase_model.p<-plm(n_banks~dyn_cum_2+turnout_percentage+enop+log(electors),data=firstphase.p)
second_phase_model_logit<-glm(data =firstphase.p, n_banks~dyn_cum_2+turnout_percentage+enop+log(electors))
second_phase_model_poisson<-glm(data =firstphase.p, n_banks~dyn_cum_2+turnout_percentage+enop+log(electors),family =  "quasipoisson")


stargazer(first_phase_model.p,second_phase_model_logit,second_phase_model_poisson,column.labels=c("OLS","LOGIT","POISSON"),no.space=TRUE,align=TRUE,type = 'html',add.lines=list(c('Year fixed effects', 'Yes','Yes','Yes')))

```
------

## Banks From 1991-2019

------
```{r,warning=FALSE,results='asis',echo=FALSE,include=TRUE,message=FALSE}
library(plm)
library(stargazer)
firstphase<-readr::read_csv("C:/Users/Jatin/Downloads/JatinCPR/Jatin NEW CPR/RBI NEW DATA/final_91.csv")

firstphase.p<-pdata.frame(firstphase,index=c("year_x"))
first_phase_model.p<-plm(n_banks~dyn_cum_2+turnout_percentage+enop+log(electors),data=firstphase.p)
second_phase_model_logit<-glm(data =firstphase.p, n_banks~dyn_cum_2+turnout_percentage+enop+log(electors))
second_phase_model_poisson<-glm(data =firstphase.p, n_banks~dyn_cum_2+turnout_percentage+enop+log(electors),family =  "quasipoisson")


stargazer(first_phase_model.p,second_phase_model_logit,second_phase_model_poisson,column.labels=c("OLS","LOGIT","POISSON"),no.space=TRUE,align=TRUE,type = 'html',add.lines=list(c('Year fixed effects', 'Yes','Yes','Yes')))

```

-------------

# PAN INDIA BANKS

* Total banks (1977-2019)-50505
* Banks Post 2009 after merging with dynasty dataset:-31430

------------

```{r,echo=FALSE,include=TRUE,message=FALSE,warning=FALSE}
#install.packages("kableExtra")
#install.packages("magrittr") # package installations are only needed the first time you use it
#install.packages("dplyr")    # alternative installation of the %>%
library(magrittr) # needs to be run every time you start R and want to use %>%
library(dplyr)
library(ggplot2)
totalseats<-readr::read_csv('C:/Users/Jatin/Downloads/JatinCPR/Jatin NEW CPR/RBI NEW DATA/state_wise_banks.csv')
totalseats <- subset(totalseats,select=-c(X1))
totalseats<-totalseats[order(totalseats$n_banks),]
ggplot(totalseats,aes(x=reorder(totalseats$pc11_state_name,-totalseats$n_banks),y=totalseats$n_banks,fill=Type))+geom_col()+coord_flip()+labs(
    y ="Banks Established", x = "State_Name")
```

-----

State wise breakup of banks post 2009

-----

```{r,echo=FALSE,include=TRUE,message=FALSE,warning=FALSE}
#install.packages("kableExtra")
#install.packages("magrittr") # package installations are only needed the first time you use it
#install.packages("dplyr")    # alternative installation of the %>%
library(magrittr) # needs to be run every time you start R and want to use %>%
library(dplyr)
library(ggplot2)
totalseats<-readr::read_csv('C:/Users/Jatin/Downloads/JatinCPR/Jatin NEW CPR/RBI NEW DATA/state_wise_banks_post_2009.csv')
totalseats <- subset(totalseats,select=-c(X1))
totalseats<-totalseats[order(totalseats$n_banks),]
ggplot(totalseats,aes(x=reorder(totalseats$pc11_state_name,-totalseats$n_banks),y=totalseats$n_banks,fill=Type))+geom_col()+coord_flip()+labs(
    y ="Banks Established", x = "State_Name")
```

-----


## Year wise breakup of banks 1977-2019

-----

```{r,echo=FALSE,include=TRUE,message=FALSE,warning=FALSE}
#install.packages("kableExtra")
#install.packages("magrittr") # package installations are only needed the first time you use it
#install.packages("dplyr")    # alternative installation of the %>%
library(magrittr) # needs to be run every time you start R and want to use %>%
library(dplyr)
library(ggplot2)
library(dplyr)
library(ggplot2)
totalseats<-readr::read_csv('C:/Users/Jatin/Downloads/JatinCPR/Jatin NEW CPR/RBI NEW DATA/year_wise_banks.csv')
totalseats <- subset(totalseats,select=-c(X1))
totalseats$year<-as.factor(totalseats$year)
ggplot(totalseats,aes(x=totalseats$year,y=totalseats$n_banks,fill=Type))+geom_col()+coord_flip()+labs(
        y ="Banks Established", x = "Year")
```

-----


## Year wise breakup of banks 2009-2019
-----

```{r,echo=FALSE,include=TRUE,message=FALSE,warning=FALSE}
#install.packages("kableExtra")
#install.packages("magrittr") # package installations are only needed the first time you use it
#install.packages("dplyr")    # alternative installation of the %>%
library(magrittr) # needs to be run every time you start R and want to use %>%
library(dplyr)
library(ggplot2)
library(dplyr)
library(ggplot2)
totalseats<-readr::read_csv('C:/Users/Jatin/Downloads/JatinCPR/Jatin NEW CPR/RBI NEW DATA/year_wise_banks_post_2009.csv')
totalseats <- subset(totalseats,select=-c(X1))
totalseats$year<-as.factor(totalseats$year)
ggplot(totalseats,aes(x=totalseats$year,y=totalseats$n_banks,fill=Type))+geom_col()+coord_flip()+labs(
        y ="Banks Established", x = "Year")
```

------

## Banks From 2009-2019

------
```{r,warning=FALSE,results='asis',echo=FALSE,include=TRUE,message=FALSE}
library(plm)
library(stargazer)
firstphase<-readr::read_csv("C:/Users/Jatin/Downloads/JatinCPR/Jatin NEW CPR/RBI NEW DATA/final_merge_pc_18_04.csv")

firstphase.p<-pdata.frame(firstphase,index=c("Year_x","State_Name"))
first_phase_model.p<-lm(n_banks~dyn,data=firstphase.p)
second_phase_model_logit<-glm(data =firstphase.p, n_banks~dyn)
second_phase_model_poisson<-glm(data =firstphase.p, n_banks~dyn,family =  "quasipoisson")


stargazer(first_phase_model.p,second_phase_model_logit,second_phase_model_poisson,column.labels=c("OLS","LOGIT","POISSON"),no.space=TRUE,align=TRUE,type = 'html',add.lines=list(c('Year fixed effects', 'Yes','Yes','Yes'), c('State fixed effects', 'Yes','Yes','Yes','Yes')))

```

-------------