---
title: Coattail Effect
author: ''
date: '2021-04-16'
slug: coattail-effect
categories: []
tags: []
---
```{r setup, include=FALSE,warning = FALSE,message=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

---


------------------------------------------------------------------------


## Index

------------------------------------------------------------------------
This index is calculated in the following manner:-For eg a party wins in a PC and then  it is calculated how many AC's it has won in the following State Elections in that PC.Supposedly it has won 2 ACs out of 7 in that PC.it is given as 2/7 Then this is  done for 543 constituencies.Score was summed and then is divided by Total Constituencies.To get the index between 0 and 100

```{r,warning = FALSE,message=FALSE}
#install.packages("kableExtra")
#install.packages("magrittr") # package installations are only needed the first time you use it
#install.packages("dplyr")    # alternative installation of the %>%
library(magrittr) # needs to be run every time you start R and want to use %>%
library(dplyr)
totalseats<-readr::read_csv('D:/OFFICE 08-04-2021/NEW STATES/SCHEDULED CASTE LOKSABHA ELECTION/newdf_13_01_2021.csv')
totalseats <- subset(totalseats,select=-c(X1))
library(kableExtra)

totalseats %>%
  kbl() %>%
  kable_material(c("striped", "hover"),full_width = FALSE)%>%kable_styling(bootstrap_options = "striped")

```
------------------------------------------------------------------------


## Indices of BJP,INC,Regional Parties

------------------------------------------------------------------------


```{r,warning = FALSE,message=FALSE}
#install.packages("kableExtra")
#install.packages("magrittr") # package installations are only needed the first time you use it
#install.packages("dplyr")    # alternative installation of the %>%
library(magrittr) # needs to be run every time you start R and want to use %>%
library(dplyr)
totalseats<-readr::read_csv('D:/OFFICE 08-04-2021/NEW STATES/SCHEDULED CASTE LOKSABHA ELECTION/partynewfinal_13_01.csv')
totalseats <- subset(totalseats)
library(kableExtra)

totalseats %>%
  kbl() %>%
  kable_material(c("striped", "hover"),full_width = FALSE)%>%kable_styling(bootstrap_options = "striped")

```



-----------------------------------------------------------------

# PROBIT REGRESSION


-----------------------------------------------------------------
* This is Probit Regression which is basically a classification problem to determine whether it won Assembly seat or not:
* Assembly Won is Categorised as Yes or No
* Indicators are Categorised as:
  + Parliament Won-PC Won[Categorised into Yes,No]
  + Year Category Assembly=StateElection Year-LokSabha Election Year
  + Party Category-National for BJP,INC.Other wise Regional




```{r,warning=FALSE,results='asis',echo=FALSE,include=TRUE,message=FALSE}
library(plm)
totalfinaldata<-readr::read_csv("D:/OFFICE 08-04-2021/NEW STATES/SCHEDULED CASTE LOKSABHA ELECTION/newdata_02_01_2021.csv")
totalfinaldata$YearCategoryAssembly<-as.factor(totalfinaldata$YearCategoryAssembly)
year_2009<-totalfinaldata[which(totalfinaldata$Year_y==2009),]
myprobit_09<- glm(AssemblyWon ~ State_Vote_Share + ParliamentWon + YearCategoryAssembly+Lok_Sabha_Vote_Share+PartyCategory, family = binomial(link = "probit"),               data = year_2009)
year_2014<-totalfinaldata[which(totalfinaldata$Year_y==2014),]
myprobit_14<- glm(AssemblyWon ~ State_Vote_Share + ParliamentWon + YearCategoryAssembly+Lok_Sabha_Vote_Share+PartyCategory, family = binomial(link = "probit"),               data = year_2014)
year_2019<-totalfinaldata[which(totalfinaldata$Year_y==2019),]
myprobit_19<- glm(AssemblyWon ~ State_Vote_Share + ParliamentWon + YearCategoryAssembly+Lok_Sabha_Vote_Share+PartyCategory, family = binomial(link = "probit"),               data = year_2019)
library(stargazer)

k1<-stargazer(myprobit_09,myprobit_14,myprobit_19,
column.labels=c("Year 2009","Year 2014","Year 2019"),
align=TRUE,type = 'html')



```

---------------------------------------------------------------------

## Predelimitation Probit Regression

```{r,warning=FALSE,results='asis',echo=FALSE,include=TRUE,message=FALSE}

totalfinaldata<-readr::read_csv("D:/OFFICE 08-04-2021/NEW STATES/SCHEDULED CASTE LOKSABHA ELECTION/finalnewdf_13_01.csv")
totalfinaldata$YearCategoryAssembly<-as.factor(totalfinaldata$YearCategoryAssembly)
year_1977<-totalfinaldata[which(totalfinaldata$Year_y==1977),]
myprobit_77<- glm(AssemblyWon ~ State_Vote_Share + ParliamentWon + YearCategoryAssembly+Lok_Sabha_Vote_Share+PartyCategory, family = binomial(link = "probit"),               data = year_1977)
year_1980<-totalfinaldata[which(totalfinaldata$Year_y==1980),]
myprobit_80<- glm(AssemblyWon ~ State_Vote_Share + ParliamentWon + YearCategoryAssembly+Lok_Sabha_Vote_Share+PartyCategory, family = binomial(link = "probit"),               data = year_1980)
year_1984<-totalfinaldata[which(totalfinaldata$Year_y==1984),]
myprobit_84<- glm(AssemblyWon ~ State_Vote_Share + ParliamentWon + YearCategoryAssembly+Lok_Sabha_Vote_Share+PartyCategory, family = binomial(link = "probit"),               data = year_1984)

year_1991<-totalfinaldata[which(totalfinaldata$Year_y==1991),]
myprobit_91<- glm(AssemblyWon ~ State_Vote_Share + ParliamentWon + YearCategoryAssembly+Lok_Sabha_Vote_Share+PartyCategory, family = binomial(link = "probit"),               data = year_1991)
year_1996<-totalfinaldata[which(totalfinaldata$Year_y==1996),]
myprobit_96<- glm(AssemblyWon ~ State_Vote_Share + ParliamentWon + YearCategoryAssembly+Lok_Sabha_Vote_Share+PartyCategory, family = binomial(link = "probit"),               data = year_1996)

year_1999<-totalfinaldata[which(totalfinaldata$Year_y==1999),]
myprobit_99<- glm(AssemblyWon ~ State_Vote_Share + ParliamentWon + YearCategoryAssembly+Lok_Sabha_Vote_Share+PartyCategory, family = binomial(link = "probit"),               data = year_1999)
year_2004<-totalfinaldata[which(totalfinaldata$Year_y==2004),]
myprobit_04<- glm(AssemblyWon ~ State_Vote_Share + ParliamentWon + YearCategoryAssembly+Lok_Sabha_Vote_Share+PartyCategory, family = binomial(link = "probit"),               data = year_2004)

library(stargazer)

k1<-stargazer(myprobit_77,myprobit_80,myprobit_84,myprobit_91,myprobit_96,myprobit_99,myprobit_04,
column.labels=c("Year 1977","Year 1980","Year 1984", "Year 1991","Year 1996","Year 1999","Year 2004"),
align=TRUE,type = 'html')



```


---------------------------------------------------------------------

# Proportion of State Assembly Seats Vs Margin of Victory for INC
---------------------------------------------------------------------

```{r,warning=FALSE,results='asis',echo=FALSE,include=TRUE,message=FALSE}
library(ggplot2)
library(dplyr)
totalfinaldata<-readr::read_csv("D:/OFFICE 08-04-2021/NEW STATES/SCHEDULED CASTE LOKSABHA ELECTION/inc_2_total.csv")

totalfinaldata %>%
    select(MOV, Proportion) %>%
    mutate(threshold = as.factor(ifelse(MOV >= 0, 1, 0))) %>%
    ggplot(aes(x = MOV, y = Proportion, color = threshold)) +
    geom_point() +
    geom_smooth(method = "loess", se = FALSE) +
    scale_color_brewer(palette = "Accent") +
    guides(color = FALSE) +
    geom_vline(xintercept = 0, color = "red",
               size = 1, linetype = "dashed") +
    labs(y = "INC State ASsembly Vote Share",
         x = "INC Margin of Victory in Lok Sabha election")



```


## Proportion of State Assembly VoteShare Vs Margin of Victory for BJP
---------------------------------------------------------------------

```{r,warning=FALSE,results='asis',echo=FALSE,include=TRUE,message=FALSE}
library(ggplot2)
library(dplyr)
totalfinaldata<-readr::read_csv("D:/OFFICE 08-04-2021/NEW STATES/SCHEDULED CASTE LOKSABHA ELECTION/bjp_2_total.csv")

totalfinaldata %>%
    select(MOV, Proportion) %>%
    mutate(threshold = as.factor(ifelse(MOV >= 0, 1, 0))) %>%
    ggplot(aes(x = MOV, y = Proportion, color = threshold)) +
    geom_point() +
    geom_smooth(method = "loess", se = FALSE) +
    scale_color_brewer(palette = "Accent") +
    guides(color = FALSE) +
    geom_vline(xintercept = 0, color = "red",
               size = 1, linetype = "dashed") +
    labs(y = "BJP State ASsembly Vote Share",
         x = "BJP Margin of Victory in Lok Sabha election")



```
