---
title: MPs Performance
author: ''
date: '2021-04-16'
slug: mps-performance
categories: []
tags: []
---

``````{r setup, include=FALSE,warning=FALSE,message=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```




------------------------------------------------------------------------


## Count of MPs(Party Wise)

------------------------------------------------------------------------
BJP,INC MPs(2004,2009,2014,2019)

```{r,warning = FALSE,message=FALSE}
#install.packages("kableExtra")
#install.packages("magrittr") # package installations are only needed the first time you use it
#install.packages("dplyr")    # alternative installation of the 
library(magrittr) # needs to be run every time you start R and want to use %>%
library(dplyr)
totalseats<-readr::read_csv('D:/OFFICE 08-04-2021/Congress PRS/t1.csv')
totalseats <- subset(totalseats)
library(kableExtra)

totalseats %>%
  kbl() %>%
  kable_material(c("striped", "hover"),full_width = FALSE)%>%kable_styling(bootstrap_options = "striped")

```
------------------------------------------------------------------------


## MPs Performance(Party Wise)

------------------------------------------------------------------------


```{r,warning = FALSE,message=FALSE}
#install.packages("kableExtra")
#install.packages("magrittr") # package installations are only needed the first time you use it
#install.packages("dplyr")    # alternative installation of the %>%
library(magrittr) # needs to be run every time you start R and want to use %>%
library(dplyr)
totalseats<-readr::read_csv('D:/OFFICE 08-04-2021/Congress PRS/t2.csv')
totalseats <- subset(totalseats,select=-c(X1))
library(kableExtra)

totalseats %>%
  kbl() %>%
  kable_material(c("striped", "hover"),full_width = FALSE)%>%kable_styling(bootstrap_options = "striped")

```
------------------------------------------------------------------------

* MPs Attendance(Party Wise)

------------------------------------------------------------------------
```{r,warning = FALSE,message=FALSE}
#install.packages("kableExtra")
#install.packages("magrittr") # package installations are only needed the first time you use it
#install.packages("dplyr")    # alternative installation of the %>%
library(magrittr) # needs to be run every time you start R and want to use %>%
library(dplyr)
library(ggthemes)
library(plotly)
totalseats<-readr::read_csv('D:/OFFICE 08-04-2021/Congress PRS/party_box.csv')
#growth_new$year_x<-as.factor(growth_new$year_x)
totalseats$ls<-as.factor(totalseats$ls)
ggplot(data=totalseats,aes(x=totalseats$`ls`, y=totalseats$Attendance,  color=totalseats$`New Party`,range=1))+geom_boxplot(outlier.shape = NA)+theme_economist()+ggtitle("Attendance Party Wise") +
    xlab("Lok Sabha") + ylab("Attendance")+labs(color='Party')
```

-----------------------------------------------------------------

* MPs Participation(Questions,Party Wise)

------------------------------------------------------------------------
```{r,warning = FALSE,message=FALSE}
#::opts_chunk$set(fig.width=12, fig.height=4) 
#install.packages("kableExtra")
#install.packages("magrittr") # package installations are only needed the first time you use it
#install.packages("dplyr")    # alternative installation of the %>%
library(magrittr) # needs to be run every time you start R and want to use %>%
library(dplyr)
library(ggthemes)
library(plotly)
totalseats<-readr::read_csv('D:/OFFICE 08-04-2021/Congress PRS/party_box.csv')
#growth_new$year_x<-as.factor(growth_new$year_x)
totalseats$ls<-as.factor(totalseats$ls)
totalseats<-totalseats[which(totalseats$Questions<700),]
ggplot(data=totalseats,aes(x=totalseats$`ls`, y=totalseats$Questions,  color=totalseats$`New Party`))+geom_boxplot(outlier.shape = NA)+ggtitle("Questions Party Wise") +
    xlab("Lok Sabha") + ylab("Questions")+labs(color='Party')+ scale_y_continuous(breaks = seq(0, 700, by = 100))+theme_economist()+scale_color_economist(name = NULL)
```

-----------------------------------------------------------------

* MPs Participation(Debates,Party Wise)

------------------------------------------------------------------------
```{r,warning = FALSE,message=FALSE}
#::opts_chunk$set(fig.width=12, fig.height=4) 
#install.packages("kableExtra")
#install.packages("magrittr") # package installations are only needed the first time you use it
#install.packages("dplyr")    # alternative installation of the %>%
library(magrittr) # needs to be run every time you start R and want to use %>%
library(dplyr)
library(ggthemes)
library(plotly)
totalseats<-readr::read_csv('D:/OFFICE 08-04-2021/Congress PRS/party_box.csv')
#growth_new$year_x<-as.factor(growth_new$year_x)
totalseats$ls<-as.factor(totalseats$ls)
totalseats<-totalseats[which(totalseats$Debates<100),]
ggplot(data=totalseats,aes(x=totalseats$`ls`, y=totalseats$Debates,  color=totalseats$`New Party`))+geom_boxplot(outlier.shape = NA)+ggtitle("Debates Party Wise") +
    xlab("Lok Sabha") + ylab("Debates")+labs(color='Party')+ theme_economist()+scale_color_economist(name = NULL)
```

-----------------------------------------------------------------

## Count of MPs(Alliance Wise)

------------------------------------------------------------------------
NDA,UPA,Others MPs(2004,2009,2014,2019)

```{r,warning = FALSE,message=FALSE}
#install.packages("kableExtra")
#install.packages("magrittr") # package installations are only needed the first time you use it
#install.packages("dplyr")    # alternative installation of the 
library(magrittr) # needs to be run every time you start R and want to use %>%
library(dplyr)
totalseats<-readr::read_csv('D:/OFFICE 08-04-2021/Congress PRS/t3.csv')
totalseats <- subset(totalseats)
library(kableExtra)

totalseats %>%
  kbl() %>%
  kable_material(c("striped", "hover"),full_width = FALSE)%>%kable_styling(bootstrap_options = "striped")

```
------------------------------------------------------------------------


## MPs Performance(Alliance Wise)

------------------------------------------------------------------------


```{r,warning = FALSE,message=FALSE}
#install.packages("kableExtra")
#install.packages("magrittr") # package installations are only needed the first time you use it
#install.packages("dplyr")    # alternative installation of the %>%
library(magrittr) # needs to be run every time you start R and want to use %>%
library(dplyr)
totalseats<-readr::read_csv('D:/OFFICE 08-04-2021/Congress PRS/t4.csv')
totalseats <- subset(totalseats,select=-c(X1))
library(kableExtra)

totalseats %>%
  kbl() %>%
  kable_material(c("striped", "hover"),full_width = FALSE)%>%kable_styling(bootstrap_options = "striped")

```
------------------------------------------------------------------------

* MPs Attendance(Alliance Wise)

------------------------------------------------------------------------
```{r,warning = FALSE,message=FALSE}
#install.packages("kableExtra")
#install.packages("magrittr") # package installations are only needed the first time you use it
#install.packages("dplyr")    # alternative installation of the %>%
library(magrittr) # needs to be run every time you start R and want to use %>%
library(dplyr)
library(ggthemes)
library(plotly)
totalseats<-readr::read_csv('D:/OFFICE 08-04-2021/Congress PRS/alliance_box.csv')
#growth_new$year_x<-as.factor(growth_new$year_x)
totalseats$ls<-as.factor(totalseats$ls)
ggplot(data=totalseats,aes(x=totalseats$`ls`, y=totalseats$Attendance,  color=totalseats$Alliance,range=1))+geom_boxplot(outlier.shape = NA)+theme_economist()+ggtitle("Attendance Alliance Wise") +
    xlab("Lok Sabha") + ylab("Attendance")+labs(color='Alliance')
```

-----------------------------------------------------------------

* MPs Participation(Questions,Alliance Wise)

------------------------------------------------------------------------
```{r,warning = FALSE,message=FALSE}
#::opts_chunk$set(fig.width=12, fig.height=4) 
#install.packages("kableExtra")
#install.packages("magrittr") # package installations are only needed the first time you use it
#install.packages("dplyr")    # alternative installation of the %>%
library(magrittr) # needs to be run every time you start R and want to use %>%
library(dplyr)
library(ggthemes)
library(plotly)
totalseats<-readr::read_csv('D:/OFFICE 08-04-2021/Congress PRS/alliance_box.csv')
#growth_new$year_x<-as.factor(growth_new$year_x)
totalseats$ls<-as.factor(totalseats$ls)
totalseats<-totalseats[which(totalseats$Questions<700),]
ggplot(data=totalseats,aes(x=totalseats$`ls`, y=totalseats$Questions,  color=totalseats$Alliance))+geom_boxplot(outlier.shape = NA)+ggtitle("Questions Alliance Wise") +
    xlab("Lok Sabha") + ylab("Questions")+labs(color='Alliance')+ scale_y_continuous(breaks = seq(0, 700, by = 100))+theme_economist()
```

-----------------------------------------------------------------

* MPs Participation(Debates,Alliance Wise)

------------------------------------------------------------------------
```{r,warning = FALSE,message=FALSE}
#::opts_chunk$set(fig.width=12, fig.height=4) 
#install.packages("kableExtra")
#install.packages("magrittr") # package installations are only needed the first time you use it
#install.packages("dplyr")    # alternative installation of the %>%
library(magrittr) # needs to be run every time you start R and want to use %>%
library(dplyr)
library(ggthemes)
library(plotly)
totalseats<-readr::read_csv('D:/OFFICE 08-04-2021/Congress PRS/alliance_box.csv')
#growth_new$year_x<-as.factor(growth_new$year_x)
totalseats$ls<-as.factor(totalseats$ls)
totalseats<-totalseats[which(totalseats$Debates<100),]
ggplot(data=totalseats,aes(x=totalseats$`ls`, y=totalseats$Debates,  color=totalseats$Alliance))+geom_boxplot(outlier.shape = NA)+ggtitle("Debates Alliance Wise") +
    xlab("Lok Sabha") + ylab("Debates")+labs(color='Alliance')+ theme_economist()
```
-----------------------------------------------------------------

## REGRESSION 
* Alliance as compared to NDA
* Education as compared to 12th Pass

* Loksabha as compared to ls14
* state type as compared to Congress and BJP

-----------------------------------------------------------------

```{r,warning=FALSE,results='asis',echo=FALSE,include=TRUE,message=FALSE}
library(plm)
totalfinaldata<-readr::read_csv("D:/OFFICE 08-04-2021/Congress PRS/totaltcpdnew.csv")
totalfinaldata$total_assets<-as.numeric(totalfinaldata$total_assets)
totalfinaldata$ls<-as.factor(totalfinaldata$ls)
totalfinaldata$Sex<-as.factor(totalfinaldata$Sex)
totalfinaldata$`Age:`<-as.numeric(totalfinaldata$`Age:`)
totalfinaldata$statetype<-as.factor(totalfinaldata$statetype)
relationpredelim <- lm(Questions~criminalcases+ls+Alliance+education+totalfinaldata$`Age:`+Candidate_Type+Sex+Turncoat+Incumbent+Recontest+No_Terms+Contested+Constituency_Type+statetype,data=totalfinaldata)
relationdebates<- lm(Debates~criminalcases+ls+Alliance+education+totalfinaldata$`Age:`+Candidate_Type+Sex+Turncoat+Incumbent+Recontest+No_Terms+Contested+Constituency_Type+statetype,data=totalfinaldata)
relationattendance <- lm(Attendance~criminalcases+ls+Alliance+education+totalfinaldata$`Age:`+Candidate_Type+Sex+Turncoat+Incumbent+Recontest+No_Terms+Contested+Constituency_Type+statetype,data=totalfinaldata)

library(stargazer)

stargazer(relationpredelim,relationdebates,relationattendance,
align=TRUE,type = 'html')
