---
title: Level of Organisation
author: ''
date: '2021-04-16'
slug: level-of-organisation
categories: []
tags: []
---
```{r set up, warning=FALSE, include=FALSE, message= FALSE }

knitr::opts_chunk$set(cache = FALSE,echo = FALSE, message=FALSE, warning = FALSE,fig.width = 16/2, fig.height = 9/2)

 
```



------------------------------------------------------------------------

# Organisation Level 

-----------------------------------------------------------------

**Data description**

* This dataset contains the level of organisation for each party in each state from 1962-2004.
* Three levels of organisation are given as:-
  + 1-Least Organised
  + 2-In Between
  + 3-Most Organised


```{r}
library(plotly)
totalfinaldata<-readr::read_csv("D:/OFFICE 08-04-2021/NEW STATES/SCHEDULED CASTE LOKSABHA ELECTION/states/states/merged_df_24_12_2020.csv")
mtcars<-totalfinaldata
mtcars$Year<-as.character(mtcars$Year)
fig <- plot_ly(mtcars, y = ~Vote_Share_Percentage, x = ~org,boxpoints="outliers", type = "box")
fig


```


# Party Analysis:Number of Units at each level for each Party

-----------------------------------------------------------------


**For INC Party**
-------
```{r}
library(plotly)
totalfinaldata<-readr::read_csv("D:/OFFICE 08-04-2021/NEW STATES/SCHEDULED CASTE LOKSABHA ELECTION/states/states/jk_inc.csv")
totalfinaldata$Phase<-as.factor(totalfinaldata$Phase)
totalfinaldata$org<-as.factor(totalfinaldata$org)
fig <- plot_ly(totalfinaldata, x = ~Phase, y = ~year,color=~org,text=totalfinaldata$year,textposition='auto')
fig <- fig %>% layout(yaxis = list(title = 'Number'), barmode = 'stack')
fig



```

-------
**For INC Party**
--------
Proportion of Each Level of Party
```{r}
library(plotly)
totalfinaldata<-readr::read_csv("D:/OFFICE 08-04-2021/NEW STATES/SCHEDULED CASTE LOKSABHA ELECTION/states/states/jk_inc.csv")
totalfinaldata$Phase<-as.factor(totalfinaldata$Phase)
totalfinaldata$org<-as.factor(totalfinaldata$org)
fig <- plot_ly(totalfinaldata, x = ~Phase, y = ~Percentage,color=~org,mode = 'text',text=totalfinaldata$Percentage, textposition = 'middle right',textfont = list(color = '#000000', size = 5))
fig <- fig %>% layout(yaxis = list(title = 'Percentage'), barmode = 'stack')
fig



```

-------
**For BJP Party**

```{r}
library(plotly)
totalfinaldata<-readr::read_csv("D:/OFFICE 08-04-2021/NEW STATES/SCHEDULED CASTE LOKSABHA ELECTION/states/states/jk_bjp.csv")
totalfinaldata$Phase<-as.factor(totalfinaldata$Phase)
totalfinaldata$org<-as.factor(totalfinaldata$org)
fig <- plot_ly(totalfinaldata, x = ~Phase, y = ~year,color=~org,text=totalfinaldata$year,textposition='auto')
fig <- fig %>% layout(yaxis = list(title = 'Number'), barmode = 'stack')
fig


```

-------
**For BJP Party**
-------- 
Proportion of Each Level of Party
```{r}
library(plotly)
totalfinaldata<-readr::read_csv("D:/OFFICE 08-04-2021/NEW STATES/SCHEDULED CASTE LOKSABHA ELECTION/states/states/jk_bjp.csv")
totalfinaldata$Phase<-as.factor(totalfinaldata$Phase)
totalfinaldata$org<-as.factor(totalfinaldata$org)
fig <- plot_ly(totalfinaldata, x = ~Phase, y = ~Percentage,color=~org,mode = 'text',text=totalfinaldata$Percentage, textposition = 'middle right',textfont = list(color = '#000000', size = 5))
fig <- fig %>% layout(yaxis = list(title = 'Percentage'), barmode = 'stack')
fig


```

-------
**For Regional Party**

```{r}
library(plotly)
totalfinaldata<-readr::read_csv("D:/OFFICE 08-04-2021/NEW STATES/SCHEDULED CASTE LOKSABHA ELECTION/states/states/jk_regional.csv")
totalfinaldata$Phase<-as.factor(totalfinaldata$Phase)
totalfinaldata$org<-as.factor(totalfinaldata$org)
fig <- plot_ly(totalfinaldata, x = ~Phase, y = ~year,color=~org,text=totalfinaldata$year,textposition='auto')
fig <- fig %>% layout(yaxis = list(title = 'Number'), barmode = 'stack')

fig

```

-------
**For Regional Party**
--------
Proportion of Each Level of Party
```{r}
library(plotly)
totalfinaldata<-readr::read_csv("D:/OFFICE 08-04-2021/NEW STATES/SCHEDULED CASTE LOKSABHA ELECTION/states/states/jk_regional.csv")
totalfinaldata$Phase<-as.factor(totalfinaldata$Phase)
totalfinaldata$org<-as.factor(totalfinaldata$org)
fig <- plot_ly(totalfinaldata, x = ~Phase, y = ~Percentage,color=~org,mode = 'text',text=totalfinaldata$Percentage, textposition = 'middle right',textfont = list(color = '#000000', size = 5))
fig <- fig %>% layout(yaxis = list(title = 'Percentage'), barmode = 'stack')
fig


```
---
# Party Analysis : Level of Organisation VS Vote %

**For INC Party**

```{r}
library(plotly)
totalfinaldata<-readr::read_csv("D:/OFFICE 08-04-2021/NEW STATES/SCHEDULED CASTE LOKSABHA ELECTION/states/states/jk1_inc.csv")
totalfinaldata$Phase<-as.factor(totalfinaldata$Phase)
totalfinaldata$org<-as.factor(totalfinaldata$org)
fig <- plot_ly(totalfinaldata, x = ~Phase, y = ~Vote_Share_Percentage,color=~org,text=totalfinaldata$Vote_Share_Percentage,textposition='auto')
fig <- fig %>% layout(yaxis = list(title = 'Vote_Share_Percentage'), barmode = 'grouped')
fig


```


**For BJP Party**

```{r}
library(plotly)
totalfinaldata<-readr::read_csv("D:/OFFICE 08-04-2021/NEW STATES/SCHEDULED CASTE LOKSABHA ELECTION/states/states/jk1_bjp.csv")
totalfinaldata$Phase<-as.factor(totalfinaldata$Phase)
totalfinaldata$org<-as.factor(totalfinaldata$org)
fig <- plot_ly(totalfinaldata, x = ~Phase, y = ~Vote_Share_Percentage,color=~org,text=totalfinaldata$Vote_Share_Percentage,textposition='auto')
fig <- fig %>% layout(yaxis = list(title = 'Vote_Share_Percentage'), barmode = 'grouped')
fig


```

**For Regional Party**

```{r}
library(plotly)
totalfinaldata<-readr::read_csv("D:/OFFICE 08-04-2021/NEW STATES/SCHEDULED CASTE LOKSABHA ELECTION/states/states/jk1_regional.csv")
totalfinaldata$Phase<-as.factor(totalfinaldata$Phase)
totalfinaldata$org<-as.factor(totalfinaldata$org)
fig <- plot_ly(totalfinaldata, x = ~Phase, y = ~Vote_Share_Percentage,color=~org,text=totalfinaldata$Vote_Share_Percentage,textposition='auto')
fig <- fig %>% layout(yaxis = list(title = 'Vote_Share_Percentage'), barmode = 'grouped')
fig


```

# Party Analysis : Mean Level of Organisation VS Mean Vote % Over the Years

**For INC Party**

```{r}
library(plotly)
totalfinaldata<-readr::read_csv("D:/OFFICE 08-04-2021/NEW STATES/SCHEDULED CASTE LOKSABHA ELECTION/states/states/jk2_inc.csv")
library(plotly)
ay <- list(
    tickfont = list(color = "red"),
    overlaying = "y",
    side = "right",
    title = "Mean Level of Organisation"
)
fig <- plot_ly()
fig <- fig %>% add_lines(x = ~totalfinaldata$Year, y = ~totalfinaldata$Vote_Share_Percentage, name = "Vote_Share")
fig <- fig %>% add_lines(x = totalfinaldata$Year, y = totalfinaldata$org, name = "Level of Organisation", yaxis = "y2")
fig <- fig %>% layout( yaxis2 = ay,
    xaxis = list(title="Year"),yaxis=list(title='Mean VoteShare'),y2=list(title='Mean Level of Organisation')
)

fig



```

**For BJP Party**

```{r}
library(plotly)
totalfinaldata<-readr::read_csv("D:/OFFICE 08-04-2021/NEW STATES/SCHEDULED CASTE LOKSABHA ELECTION/states/states/jk2_bjp.csv")
library(plotly)
ay <- list(
    tickfont = list(color = "red"),
    overlaying = "y",
    side = "right",
    title = "Mean Level of Organisation"
)
fig <- plot_ly()
fig <- fig %>% add_lines(x = ~totalfinaldata$Year, y = ~totalfinaldata$Vote_Share_Percentage, name = "Vote_Share")
fig <- fig %>% add_lines(x = totalfinaldata$Year, y = totalfinaldata$org, name = "Level of Organisation", yaxis = "y2")
fig <- fig %>% layout( yaxis2 = ay,
    xaxis = list(title="Year"),yaxis=list(title='Mean VoteShare'),y2=list(title='Mean Level of Organisation')
)

fig





```

**For Regional Party**

```{r}
library(plotly)
totalfinaldata<-readr::read_csv("D:/OFFICE 08-04-2021/NEW STATES/SCHEDULED CASTE LOKSABHA ELECTION/states/states/jk2_regional.csv")
library(plotly)
ay <- list(
    tickfont = list(color = "red"),
    overlaying = "y",
    side = "right",
    title = "Mean Level of Organisation"
)
fig <- plot_ly()
fig <- fig %>% add_lines(x = ~totalfinaldata$Year, y = ~totalfinaldata$Vote_Share_Percentage, name = "Vote_Share")
fig <- fig %>% add_lines(x = totalfinaldata$Year, y = totalfinaldata$org, name = "Level of Organisation", yaxis = "y2")
fig <- fig %>% layout( yaxis2 = ay,
    xaxis = list(title="Year"),yaxis=list(title='Mean VoteShare'),y2=list(title='Mean Level of Organisation')
)
fig





```

# Mean Org Vs Mean Vote Share %
```{r}
totalfinaldata<-readr::read_csv("D:/OFFICE 08-04-2021/NEW STATES/SCHEDULED CASTE LOKSABHA ELECTION/states/states/totalnewparty.csv")
pl = ggplot(totalfinaldata, aes(x=org, y=Vote_Share_Percentage)) +
  theme_bw() +theme (panel.border = element_blank(),
       axis.line= element_line(color='white'),strip.background = element_blank())+
  geom_point(shape=16, 
             color = 'black',
             alpha = 1) +
  
  geom_smooth(method='lm',varwidth=TRUE)+ labs(y="Vote %", x = "Mean Org")
pl + facet_wrap(.~PartyNEW,ncol=3,scales="free_x")
```

